DRAFT: Scalable, Robust Multipath Communication on the Butterfly Network

### 2018-05-21 plosone/attack.tex
Change description of bounded trust.

We consider a setting in which a source node attempts to route a message
to a target node, while an adversary attempts to block or intercept the message
by compromising a number of intermediate nodes.
We also assume that edges represent {\em direct trust},
i.e., the belief that an adversary is unlikely to compromise a neighbor,
as in the web of trust approach
\cite{zimmermann_official_1995,richters_trust_2011}.
The web of trust approach requires infinite trust transitivity in that
for one node to trust another,
at least one path of direct trusted edges must exist between them.
The assumption of infinite transitivity is unrealistic
\cite{christianson_why_1997},
so we instead make a stricter assumption: {\em bounded trust transitivity},
that trust transitivity can only be extended over a finite number of edges.
Even with this more restrictive assumption, we show how trust can be established
between two nodes even when no path of directly trusted edges exists between them.

>>>>

We consider a setting in which a source node attempts to route a message
to a target node, while an adversary attempts to block or intercept the message
by compromising a number of intermediate nodes.
We also assume that edges represent {\em direct trust},
i.e., the belief that an adversary is unlikely to compromise a neighbor,
as in the web of trust approach
\cite{zimmermann_official_1995,richters_trust_2011}.
The web of trust approach typically assumes infinite trust transitivity in that
it is possible for one node to have some level of trust for another as long
as they are connected by a path of directly trusted edges,
regardless of the length of that path.
The assumption of infinite transitivity is unrealistic
\cite{christianson_why_1997},
so we instead make a stricter assumption: {\em bounded trust transitivity},
that trust transitivity can only be extended over a finite number of edges.
Even with this more restrictive assumption, we show how trust can be established
between two nodes even when no path of directly trusted edges exists between them.
